### 2017-06-12 README.Rmd
Change hypothesis to hypothesize and add Two Proportions example

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesis(null = "p = 25") %>% # would require string parsing
  generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
  calculate(stat = "prop") #
```

Two categorical (2 level) variables
```
mtcars %>%
  select(am, vs) %>%
  hypothesis(null = "independence") %>% # 
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in prop") #
```

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesis(null = "p1 = .33, p2 = .33, p3 = .33") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables
```
mtcars %>%
  select(cyl, am) %>%
  hypothesis(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

One numerical variable one categorical (2 levels) (diff in means)
```
mtcars %>%
  select(mpg, am) %>%
  hypothesis(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

One numerical one categorical (>2 levels) -  ANOVA
```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesis(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR
```
mtcars %>%
  select(mpg, hp) %>%
  hypothesis(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "lm(mpg ~ hp)")
```

>>>>

***

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "p = 25") %>% # would require string parsing
  generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
  calculate(stat = "prop") #
```

Two categorical (2 level) variables

- Implemented

```
mtcars %>%
  select(am, vs) %>%
  hypothesize(null = "independence") %>% # 
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props") #
```

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "p1 = .33, p2 = .33, p3 = .33") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables
```
mtcars %>%
  select(cyl, am) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

One numerical variable one categorical (2 levels) (diff in means)

- Implemented

```
mtcars %>%
  select(mpg, am) %>%
  hypothesize(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

One numerical one categorical (>2 levels) -  ANOVA
```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesize(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR
```
mtcars %>%
  select(mpg, hp) %>%
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "lm(mpg ~ hp)")
```
